# Smoothing

```{r}
library(tidyverse)
library(tsibble)
library(feasts)
library(readxl)
```

## Example 1.1

### Data

Create a data frame.

```{r}
forest_fire <- tribble(
  ~year, ~cnt,
  2006, 369,
  2007, 418,
  2008, 389,
  2009, 570,
  2010, 282,
  2011, 277,
  2012, 197,
  2013, 296,
  2014, 492,
  2015, 623,
  2016, 391
)
```

### Convert to time-series data

Convert the data frame to time series data frame (`tsibble`) object. You must set `index` with a column that represents timepoints for the series. Please note that `tsibble` automatically notice that the index is year and that the series is regular yearly series.

```{r}
forest_fire_ts <-
  forest_fire |>
  as_tsibble(index = year)

forest_fire_ts
```


### Moving average

Compute moving average by calling `slider::slide_mean()`. Set `complete = TRUE` to return missing value `NA` when there are missing observations in the sliding window.

```{r}
forest_fire_ma <-
  forest_fire_ts |>
  mutate(
    ma3 = slider::slide_mean(cnt, before = 2, after = 0, complete = TRUE),
    ma6 = slider::slide_mean(cnt, before = 5, after = 0, complete = TRUE)
  )

forest_fire_ma
```

Now, `forest_fire_ma` is a time series data frame with three series: original value `cnt`, 3-yr moving average `ma3`, and 6-yr moving average `ma6`. 


### Visualization

Covert this to a long form by calling `pivot_longer()`. The resulting time series data frame will have `key` that is a label of each series.

```{r}
forest_fire_ma_long <- 
  forest_fire_ma |>
  pivot_longer(c(cnt, ma3, ma6), names_to = "statistics")

forest_fire_ma_long
```


Visualize time series data. Call `autoplot()` with measurement variable name to draws line plot by each `key`.

```{r}
forest_fire_ma_long |> 
  autoplot(value)
```


## Example 1.2

### Load data

```{r}
household <- 
  read_excel("data/J01.xlsx", skip = 1) |> 
  rename(cnt = `#households`)
```

### Convert to time-series data

```{r}
household_ts <-
  household |> 
  as_tsibble(index = year)

household_ts
```


### Train/test split

```{r}
household_ts_train <-
  household_ts |> 
  filter(year <= 2014)

household_ts_test <-
  household_ts |> 
  filter(year > 2014)
```


### Double moving average with N = 4

```{r}
N <- 4

household_double_ma <-
  household_ts_train |> 
  mutate(
    ma = slider::slide_mean(cnt, before = N - 1, after = 0, complete = TRUE),
    ma_double = slider::slide_mean(ma, before = N - 1, after = 0, complete = TRUE)
  )

household_double_ma
```

Visualize results.

```{r}
household_double_ma |> 
  pivot_longer(c(cnt, ma, ma_double), names_to = "statistics") |> 
  autoplot(value)
```


### Estimate a slope

Take the latest moving average and double moving average.

```{r}
latest <- 
  household_double_ma |> 
  slice_tail(n = 1)

latest
```

Compute a slope

```{r}
b <- (latest$ma - latest$ma_double) / (N - 1) * 2
b
```


### Prediction

```{r}
household_ts_test |> 
  mutate(
    ma = latest$ma,
    ma_double = 2 * latest$ma - latest$ma_double + (year - latest$year) * b
  )
```

