# Stationary time series

```{r}
library(tidyverse)
library(tsibble) # time series data frame wrangling
library(fable)   # forecasting models
library(feasts)  # feature extraction, statistics, visualization for time series data
library(readxl)
```


## Examples 2.2, 2.4

### Load data

```{r}
earthquake <-
  read_excel("data/J08.xlsx", skip = 1, n_max = 50) |>
  mutate(year = year(year)) |>
  as_tsibble(index = year)
earthquake
```

### Sample mean and sample variance

Sample size:

```{r}
n <- nrow(earthquake)
```

Sample mean: 

```{r}
z_bar <- mean(earthquake$numbers)
z_bar
```

Sample variance:

```{r}
gamma_0 <- var(earthquake$numbers)
gamma_0
```

### Ex 2.2: Autocorrelation function

Use `n - 1` as denominator for covariance.

$$
\hat{\gamma}(k) = \frac{1}{n - 1} \sum_{i=k+1}^{n} (z_i - \bar{z})(z_{i-k} - \bar{z})
$$

$$
\hat{\rho}(k) = \hat{\gamma}(k) / \hat{\gamma}(0)
$$

```{r}
K <- 10 # maximum lag

rho <- map_dbl(
  seq_len(K),
  \(k) sum((earthquake$numbers[(k+1):n] - z_bar) * 
           (earthquake$numbers[1:(n-k)] - z_bar)) / 
           (n - 1) / gamma_0
)
rho
```

#### Use `stats::acf()`

`{stats}`, one of R's core package, provides `acf()` function to compute autocorrelation.

```{r}
acf_results <- acf(earthquake$numbers, type = "correlation", plot = FALSE, lag.max = K)
acf_results
```


#### Use `feasts::ACF()`

`{feasts}`, a part of tidyverts framework, provide `ACF()` function to compute autocorrelation on `tsibble` object.

```{r}
earthquake |> 
  ACF(numbers, lag_max = K)
```

Visualize autocorrelation function.

```{r}
earthquake |> 
  ACF(numbers, lag_max = K) |> 
  autoplot()
```



### Ex 2.4: Partial autocorrelation function

```{r}
x <- acf_results$acf[c(
  rev(seq_len(K - 1) + 1), 1, seq_len(K - 1) + 1)]
y <- acf_results$acf[seq_len(K) + 1]

mat <- reduce(
  setdiff(seq_len(K), 1),
  \(m, i) rbind(m, x[(K - i) + seq_len(K)]),
  .init = x[(K - 1) + seq_len(K)]
)

map_dbl(
  seq_len(K),
  \(k) solve(mat[1:k, 1:k], y[1:k])[k]
)
```


#### Use `stats::pacf()`

```{r}
pacf(earthquake$numbers, lag.max = K, plot = FALSE)
```

#### Use `feasts::PACF()`

```{r}
earthquake |> 
  PACF(numbers, lag_max = K)
```

Visualize partial autocorrelation function.

```{r}
earthquake |> 
  PACF(numbers, lag_max = K)
```