# Stationary time series

```{r}
library(tidyverse)
library(tsibble) # time series data frame wrangling
library(fable)   # forecasting models
library(feasts)  # feature extraction, statistics, visualization for time series data
library(readxl)
```


## Examples 2.2, 2.4

### Load data

```{r}
earthquake <-
  read_excel("data/J08.xlsx", skip = 1, n_max = 50) |>
  mutate(year = year(year)) |>
  as_tsibble(index = year)
earthquake
```

### Sample mean and sample variance

Sample size:

```{r}
n <- nrow(earthquake)
```

Sample mean: 

```{r}
z_bar <- mean(earthquake$numbers)
z_bar
```

Sample variance:

```{r}
gamma_0 <- var(earthquake$numbers)
gamma_0
```

### Ex 2.2: Autocorrelation function

Use `n - 1` as denominator for covariance.

```{r}
rho <- map_dbl(
  1:10,
  \(k) sum((earthquake$numbers[(k+1):n] - z_bar) * 
           (earthquake$numbers[1:(n-k)] - z_bar)) / 
           (n - 1) / gamma_0
)
rho
```

#### Use `stats::acf()`

`{stats}`, one of R's core package, provides `acf()` function to compute autocorrelation.

```{r}
acf_results <- acf(earthquake$numbers, type = "correlation", plot = FALSE, lag.max = 10)
acf_results
```


#### Use `feasts::ACF()`

`{feasts}`, a part of tidyverts framework, provide `ACF()` function to compute autocorrelation on `tsibble` object.

```{r}
earthquake |> 
  ACF(numbers, lag_max = 10)
```


### Ex 2.4: Partial autocorrelation function

```{r}
x <- c(acf_results$acf[10:2], acf_results$acf[1:10])
y <- acf_results$acf[2:11]

mat <- reduce(
  2:10,
  \(m, i) rbind(m, x[(10 - i) + (1:10)]),
  .init = x[10:19]
)

map_dbl(
  1:10,
  \(k) solve(mat[1:k, 1:k], y[1:k])[k]
)
```

#### Use `stats::pacf()`

```{r}
pacf(earthquake$numbers, lag.max = 10, plot = FALSE)
```

#### Use `feasts::PACF()`

```{r}
earthquake |> 
  PACF(numbers, lag_max = 10)
```

