# ARMA identification and estimation

```{r}
library(tidyverse)
library(tsibble) # time series data frame wrangling
library(fable)   # forecasting models
library(feasts)  # feature extraction, statistics, visualization for time series data
library(readxl)
```

## Example 4.1

### Data

```{r}
ts <- 
  tsibble(
    t = 1:15,
    value = c(-1.01, -0.81, -0.33, -0.40, -0.95, -1.33, 0.72, 0.63,
               1.30, 1.08, -0.33, 0.31, 0.10, -0.41, -0.22),
    index = t
  )
```

### ACF

```{r}
ts |> 
  ACF(value)
```

### PACF

```{r}
ts |> 
  PACF(value)
```


## Examples 4.2, 4.7 - 4.8

### Load data

```{r}
nile_flow <- read_excel(
  "data/J09.xlsx", 
  n_max = 99, 
  .name_repair = janitor::make_clean_names
) |> 
  mutate(year = 1872:1970) |> 
  as_tsibble(index = year)
```


```{r}
nile_flow |> 
  autoplot(mean_flow)
```


### Ex 4.2: Model identification

#### ACF

```{r}
nile_flow |> 
  ACF(mean_flow) |> 
  autoplot()
```

#### PACF

```{r}
nile_flow |> 
  PACF(mean_flow) |> 
  autoplot()
```


### Ex 4.7: Model estimation

Use `AR()` from `{fable}` package. In formula, use `order(2)` set the order of auto-regressive term to be 2.

```{r}
ar_fit <- 
  nile_flow |> 
  model(AR = AR(mean_flow ~ order(2)))

ar_fit
```

:::{.callout-note}
Use `order()` without argument if you want to let the order of auto-regressive term to be optimized based on information criterion.
:::


See the estimated model.

```{r}
report(ar_fit)
```

See more detailed statistics of the regression coefficients.

```{r}
tidy(ar_fit)
```

See model-level statistics.

```{r}
glance(ar_fit)
```


### Ex 4.8: Residual diagnostics

```{r}
ar_fit |> 
  augment() |> 
  features(.innov, ljung_box, lag = 12)
```

